%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=1in, top=1in, right=1in, bottom=2cm, footskip=.5cm} % Configure page margins with geometry

\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-red} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Google}{Application}
\address{Apartment 10, No.10 Xitucheng Road, Beijing University of Posts and Telecommunications, Haidian District, Beijing, PRC \\Postal number: 100876}
\mobile{(+86) 137-1797-8744}

\email{yidawang.cn@gmail.com}
\homepage{www.researchgate.net/profile/Yida\_Wang}
\github{Wangyida}
\linkedin{Yida Wang}
\skype{Yida Wang}
\stackoverflow{6844155}{yida-wang}
%\twitter{@twit}

\position{Master Student{\enskip\cdotp\enskip}Pattern Recognition and Intelligent System} % Your expertise/fields
%\quote{``Proudly Enrolled in PRIS Lab of BUPT."} % A quote or statement

\makecvfooter{\today}{Yida Wang~~~·~~~Résumé}{\thepage} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{Company Recruitment Team}{Initech Inc.\\4120 Freidrich Ln.\\Austin, TX 78744} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Job Application for Middle Manager} % The title of the letter

\letteropening{Dear Mr./Ms./Dr. LastName,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

\letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter

\makecvfooter{\today}{Yida Wang~~~·~~~Personal Statement}{\thepage} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed

%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header


\lettersection{Goal for Brain Residency}

I am Yida Wang, first ranking master student among 760 students in 2016 who study in Beijing University of Posts and Telecommunications. My major of electronic and communication engineering in this school also ranks in the first position among all other universities in China. I have been doing research on Machine Learning and Computer Vision for more than 2 years and information theories for 6 years. I'm seeking the opportunity to be a Brain Residency researcher from fall of 2017. I think my ability and experience on machine learning and computer vision are solid for my future research and also valuable for new team, so I'm eager to be a part of wonderful team in field of computer vision and machine learning including deep learning. My interests on pursuing this position comes from previous research and projects experience on machine learning based on computer vision but not limited to it. I am also eager to enhancing my ability on statistical math and generative model in this period. I'm looking forward to get your response and interview if you have interest on my ability. I attach my Resume and publications as the attachments for detailed information.

It is so amazing that I can share my own contributions with other researchers all around the world through my publications and try to make ideas come true through supporting open source projects. For the aim of being more capable in artificial intelligence and machine learning, I started my researches through computer vision related topics such as biometric recognition because computer vision related topics are more instinct for human beings such as research students like me. Now I am going to dig deeper in the combination of basic mathematics and machine learning. Finishing such a great project in a wonderful group is not just a goal for an achievement for me, it's rather the best chance for me to seek knowledge on my favorite area and contribute better works together with other excellent co-workers.

\lettersection{About Me}

I have both experience and passion on CV and AI research including publishing several papers as first author in popular conferences and journals such as ICIP, CCBR and ACCV with the guidance of my adviser Dr. Weihong Deng from Pattern Recognition and Intelligent System Laboratory of Beijing University of Posts and Telecommunications. I am the only one in my group this year to accept the highest honor for the National Scholarship for master students of China for my research of 2016 while my other academic achievements are listed in my Resume. I value contributions from great people much, so I always use open source tools to develop mathematic models and codes written by myself to help carry out my own researches rather than using pirated softwares. Knowledge on mathematics and programming are two cornerstones for my previous and future research.

For projects experiences, I’m invited by Dr. Judith Bishop from Microsoft Research Redmond for a presentation on Microsoft Faculty Summit 2016 because I received the global 2nd prize in deep learning challenge. I am also one of a project member of deep learning toolbox: tiny-dnn with the help of my mentor Dr. Stefano Fabri and Manuele Tamburrano from Consorzio Roma Ricerche because I had internship with OpenCV for 2 summers from 2015 to 2016 in Computer Vision and also been involving in practical machine learning with sponsorship from Google within these 2 years. So my experience is not just limited to computer vision related topics, but also other techniques or algorithms such as 3D models utilization techniques and large scale text data analysis.

My previous works are supported by really fantastic people who I am so grateful for in these years. I have recommendation from Associate Professor Dr. Weihong Deng of Beijing University of Posts and Telecommunications, Dr. Gary Bradski who is Founder/CEO of OpenCV and Dr. Stefano Fabri who is Lab Chief of Consorzio Roma Ricerche. Dr. Deng helped me a lot in my school related stuffs including paper working while Dr. Fabri and Dr. Bradski keep giving me good guidance on applicable coding techniques and latest frontier technical ideas in machine learning. I have just tried one time for TOEFL and GRE and I will definitely make them higher in next time cause I am really much more crazy about my research experiments in the last month. I have attended conferences and have speeches in the US twice in this year, so I don't think my ability on English is not good. I have also been working and communicating with foreign friends and researchers in English for at least 2 years with 2 letters of verification letters from Google to certify that I have been involved with Google sponsored projects for at least 8 months as summer internship with international scientific communities.

In the end, I also have personal achievements on non-academic areas. As an athlete of University track and field team for 7 years, I won the medals both in national and interstate competition more than once, I know how to deal with competition and cooperation with a team, so I'm sure that I will be a qualified part of an academic research team also. It's not so easy to balance the life of training for physical competition and academic research for general people, but I deal with it well to make them able to be supported by each other and make myself and my works perfect with my passion.

%----------------------------------------------------------------------------------------

\end{document}
