%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{论文-}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

\cventry
{Yida Wang, David Joseph Tan, Nassir Navab, Federico Tombari} % Role
{SoftPoolNet: Shape Descriptor for Point Cloud Completion and Classification} % Title
{Euro. Conf. Computer Vision (\textit{oral})} % Location
{\href{https://www.youtube.com/watch?v=zw4NlyxWlBg}{\color{awesome-skyblue}{\underline{online demo}}} 2020} % Date(s)
{ % Description(s)
}

\cventry
{Yanyan Li, Nikolas Brasch, Yida Wang, Nassir Navab, Federico Tombari} % Role
{Structure-SLAM: Low-Drift Monocular SLAM in Indoor Environments} % Title
{IEEE/RSJ Int. Conf. Intelligent Robots and Systems} % Location
{2020} % Date(s)
{ % Description(s)
}

\cventry
{Yida Wang, David Joseph Tan, Nassir Navab, Federico Tombari} % Role
{ForkNet: Multi-branch Volumetric Semantic Completion from a Single Depth Image} % Title
{IEEE Int. Conf. Computer Vision} % Location
{\href{https://www.youtube.com/watch?v=1WZ16bGff1o}{\color{awesome-skyblue}{\underline{online demo}}} 2019} % Date(s)
{ % Description(s)
}

\cventry
{Yida Wang, Yafei Gao, Pietro Falco, Nassir Navab, Federico Tombari} % Role
{Variational Object-aware 3D Hand Pose from a Single RGB Image} % Title
{IEEE Robot. Autom. Lett.} % Location
{\href{https://www.youtube.com/watch?v=tSTQ2NTqB4A}{\color{awesome-skyblue}{\underline{online demo}}} 2019} % Date(s)
{ % Description(s)
}

\cventry
{Yida Wang, David Joseph Tan, Nassir Navab and Federico Tombari} % Role
{Adversarial Semantic Scene Completion from a Single Depth Image} % Title
{IEEE Int. Conf. 3D Vision} % Location
{\href{https://www.youtube.com/watch?v=udvBhkupwXE&t=1s}{\color{awesome-skyblue}{\underline{online demo}}} 2018} % Date(s)
{ % Description(s)
}

\cventry
{Yida Wang and Weihong Deng} % Role
{Generative Model with Coordinate Metric Learning for Object Recognition Based on 3D Models} % Title
{IEEE Trans. Image Processing} % Location
{2018} % Date(s)
{ % Description(s)
}

%------------------------------------------------

\cventry
{Yida Wang, Can Cui and Weihong Deng} % Role
{ZigzagNet: Efficient Deep Learning for Real Object Recognition Based on 3D Models} % Title
{Asian Conf. Computer Vision} % Location
{2016} % Date(s)
{ % Description(s)
%\begin{cvitems}
%\item {Conference paper.}
%\end{cvitems}
}

%------------------------------------------------

\cventry
{Yida Wang and Weihong Deng} % Role
{Self-restraint Object Recognition by Model Based CNN Learning} % Title
{IEEE Int. Conf. Image Processing} % Location
{2016} % Date(s)
{ % Description(s)
%\begin{cvitems}
%\item {Conference paper.}
%\end{cvitems}
}

%------------------------------------------------

\cventry
{Yida Wang} % Role
{CNTK on Mac: 2D Object Restoration and Recognition Based on 3D Model} % Title
{Microsoft Faculty Summit 2016} % Location
{\href{https://www.microsoft.com/en-us/research/academic-program/microsoft-open-source-challenge/}{\color{awesome-skyblue}{\underline{link}}} 2016} % Date(s)
{ % Description(s)
%\begin{cvitems}
%\item {Conference paper.}
%\end{cvitems}
}
%------------------------------------------------

\cventry
{Co-­author} % Role
{Large-Scale 3D Shape Retrieval from ShapeNet Core55} % Title
{EG 2016 workshop on 3D} % Location
{2016} % Date(s)
{ % Description(s)
}

%------------------------------------------------

\cventry
{Yida Wang, Manuele Tamburrano and Stefano Fabri} % Role
{Tutorial on 3D object pose estimation \& super resolution} % Title
{OpenCV 3 and 4} % Location
{\href{https://docs.opencv.org/master/d2/d42/tutorial_table_of_content_cnn_3dobj.html}{\color{awesome-skyblue}{\underline{link}}} 2015, 2019} % Date(s)
{ % Description(s)
%\begin{cvitems}
%\item {Conference paper.}
%\end{cvitems}
}
%------------------------------------------------

\cventry
{Yida Wang, Shasha Li, Jiani Hu and Weihong Deng} % Role
{Face Recognition Using Local PCA Filters} % Title
{CCBR 2015} % Location
{2015} % Date(s)
{ % Description(s)
%\begin{cvitems}
%\item {Conference paper.}
%\end{cvitems}
}

%------------------------------------------------

\end{cventries}
