%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=1in, top=1in, right=1in, bottom=2cm, footskip=.5cm} % Configure page margins with geometry

\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-red} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Personal}{History}
\address{Apartment 10, No.10 Xitucheng Road, Beijing University of Posts and Telecommunications, Haidian District, Beijing, PRC \\Postal number: 100876}
\mobile{(+86) 137-1797-8744}

\email{yidawang.cn@gmail.com}
\homepage{www.researchgate.net/profile/Yida\_Wang}
\github{Wangyida}
\linkedin{Yida Wang}
\skype{Yida Wang}
\stackoverflow{6844155}{yida-wang}
%\twitter{@twit}

\position{Master Student{\enskip\cdotp\enskip}Pattern Recognition and Intelligent System} % Your expertise/fields
%\quote{``Proudly Enrolled in PRIS Lab of BUPT."} % A quote or statement

\makecvfooter{\today}{Yida Wang~~~·~~~Résumé}{\thepage} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{Company Recruitment Team}{Initech Inc.\\4120 Freidrich Ln.\\Austin, TX 78744} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Job Application for Middle Manager} % The title of the letter

\letteropening{Dear Mr./Ms./Dr. LastName,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

\letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter

\makecvfooter{\today}{Yida Wang~~~·~~~Personal Statement}{\thepage} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed

%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header


\lettersection{Now}

I am Yida Wang, 1st-ranking master student in 2016 among 760 students who study in Beijing University of Posts and Telecommunications majors in the 1st-ranking major in China. I accepted the highest honor for the National Scholarship in China for my research of 2016 together with several other academic achievements which are listed in my Resume. As track and field university athlete, I have wan gold and bronze medals in Beijing City and Asia. Although I'm still not so satisfied with my current works and achievements, I do appreciate my hard working personality and independent thought in previous time with full passion for what I concerns most.

\lettersection{Back to the beginning}

I am born in northern region of China where winter is really cold and atmosphere is so dry. I am always outstanding among other students from elementary school to senior high school in my hometown. High educational entrance exam in China is really hard to get a high score for students through out China in that age and I got the highest score in my province among those students from my hometown in current university. Someone ever asked me whether it is still going on well to be top student as smoothly as before for me in the next four years in university, but I must admit that the answer is 'No'. I found that students from south region of China is smarter than ones from the north, so they react faster and doing homework in higher quality. In the beginning of my campus life, my ranking dropped from the real top to the middle in campus in the first year of my undergraduate degree. But at the same time, I learned a lot of brand new stuffs both in academic area and non-academic aspects. Finally, I found that their advantages came from solid previous knowledge and flexible ideas for new stuffs, so I tried my best to catch up with those really top students in the following 2 years and kept getting much more achievement than what I have thought about before. If someone ask me now when I got my first ranking again? I will answer that it's 6 years later in the same school. So I just passed a valley in academic stuffs in previous 6 years from 1st to just first fifty percent and back to the first. Now I don't mind some ranking like judgement in my academic life, I think all my efforts deserve when I am devoted to something which I have passion on.

I think what keep me seeking for the ultimate science and carrying out fantastic projects in university is my own passion and the precious help from friends. I never give up on something and also seldom have a depressed mood even when I fail, so I just keep doing my current works and try my best to makes goals come true. I am also an semi-professional athlete in track and field team of Beijing University of Posts and Telecommunications since I entered this school with several medals including a gold for '400 meters' by continuous training for 6 years. Such experience also give me a tough personality and clear mind for what I am dealing with which is also applicable for my research life.

I find that machine learning and artificial intelligence is really fantastic when I started to choose my master major, so I asked for Dr. Weihong Deng whether he could be my advisor in the future because I know that he is a really skillful and earnest professor in pattern recognition area who has ever publish papers in Science. His kindness for me finally gave me the chance to be involved with his team and he also thought that I have pretty good potential research ability and passion. He do this favor for me when I just ranked in the first 20 percent in the end of my undergraduate year while his previous students are almost all first 2 percent in the whole university. I was really grateful for him and kept doing my researches well in the following 2.5 years for master degree, so at the same time my achievements and abilities in this area are climbing up so fast compared with before. Rank of me is back to the 1st in general statistic result of my school and I also had some high quality papers together with mature open source projects in the last half year of my master degree researching time.

\lettersection{Future}

Now I am seeking for the bright future on researches in machine learning and artificial intelligence area in the US. I will keep moving and seeking together with friends and guiders in fancy team. My goal for getting better academic achievements and making more popular projects will never change.

It is so amazing that I can share my own contributions with other researchers all around the world through my publications and try to make ideas come true through supporting open source projects. For the aim of being more capable in artificial intelligence and machine learning, I started my researches through computer vision related topics such as biometric recognition because computer vision related topics are more instinct for human beings such as research students like me. Now I am going to dig deeper in the combination of basic mathematics and machine learning. Finishing PhD in a great group is not just a goal for a degree for me, it's rather the best chance for me to seek knowledge on my favorite area and contribute better works together with other excellent labmates.
%------------------------------------------------


\end{document}
